### 2017-07-01 motivation.tex
RR Figures added.

>>>>

\begin{figure}[t]
\includegraphics[scale=0.5]{Figures/RR-postgres}
\caption{Database state transitions corresponding to an execution of
  an RR transaction $T_1$ on Postgres. $T_2$ and $T_3$ are concurrent
  transactions. State has three data items, $a$, $b$ and $c$. }
\label{fig:rr-postgres}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.5]{Figures/RR-abstract}
  \caption{An abstract execution equivalent to the one in
  Fig.~\ref{fig:rr-postgres}. Database state remains invariant as long as
  $T_1$ executes. The effects of concurrent transactions ($T_2$ and
  $T_3$) are witnessed just before the commit.}
\label{fig:rr-abstract}
\end{figure}
